On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-14 manuscripts/PNAS/chazthm_pnas.tex
more edits appendix

The desired result, \eqref{DTILeq}, now follows by bounding the second term on the right-hand side using the following fact \cite[Thm.~9.33]{Deutsch12}:
\begin{align}
\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2,
\end{align}
for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}, recalling $\theta$ from Def.~\ref{FriedrichsDefinition}. Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this yields:
\begin{align*}
\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2 
&= \|\left( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V \right) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \\
&\leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2.
\end{align*}

@@

\begin{proof}
Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg(i)$. Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would lead us to conclude that there are more than $\deg(1)$ sets in $\mathcal{H}$ sharing a common element. %QUESTION: Do we really need to say this..?

@@

\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$. % for space:  (e.g.,  \cite{folland2013real}). 
By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero whenever $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, this property (stability) holds with probability one.
\end{proof}

>>>>

The desired result, \eqref{DTILeq}, now follows by bounding the second term on the right-hand side using the following fact \cite[Thm.~9.33]{Deutsch12}:
\begin{align}
\|\Pi_{V_k}\Pi_{V_{k-1}}\cdots\Pi_{V_1} \mathbf{x} - \Pi_V\mathbf{x}\|_2 \leq z \|\mathbf{x}\|_2,
\end{align}
for \mbox{$z^2= 1 - \prod_{\ell =1}^{k-1}(1-z_{\ell}^2)$} and \mbox{$z_{\ell} = \cos\theta\left(V_{\ell}, \cap_{s=\ell+1}^k V_s\right)$}, recalling $\theta$ from Def.~\ref{FriedrichsDefinition}. Together with $\Pi_{V_\ell} \Pi_V = \Pi_V$ for all $\ell \in [k]$ and $\Pi_V^2 = \Pi_V$, this implies that $\|\Pi_{V_k} \cdots \Pi_{V_1}\mathbf{x}  - \Pi_V \mathbf{x} \|_2$ satisfies:
\[\| ( \Pi_{V_k} \cdots\Pi_{V_1} - \Pi_V ) (\mathbf{x} - \Pi_V\mathbf{x})\|_2 \leq z\|\mathbf{x} - \Pi_V\mathbf{x}\|_2.\]

@@

\begin{proof}
Consider the collection of pairs: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg(i)$. Note that assumption \eqref{cond} implies $\bar m \geq |T_1| / \deg(1)$, since otherwise pigeonholing the elements of $T_1$ with respect to their set of possible first indices $[\bar m]$ would contradict that there are more than $\deg(1)$ sets in $\mathcal{H}$ sharing a common element. %QUESTION: Do we really need to say this..?

@@

\begin{proof}[Proof (sketch) of Cor.~\ref{ProbabilisticCor}]
First, note that if a set of measure spaces $\{(X_{\ell}, \Sigma_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has that $\nu_{\ell}$ is absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$. % for space:  (e.g.,  \cite{folland2013real}). 
By Thm.~\ref{robustPolythm}, there is a polynomial that is nonzero when $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$; in particular, stability holds with probability one.
\end{proof}
